InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
Falcon section

The first image generative model we use is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.

Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders. Due to its work directly in pixel space, they are very computational expensive. To lower the computational costs, the Stable Diffusion model is applied in a latent space of powerful pretrained autoencoders. This works without losing quality and flexibility. \cite{Rombach_2022_CVPR}

>>>>

The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models. Its is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set. This data set leverages strict filtering and stringent deduplication to uplift the quality of web data. \cite{penedo2023refinedweb}
